---
title: "Statistical Simulation: Midterm II"
author: "H24071320"
output: 
  html_document:
  #pdf_document:
  code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#set.seed("the last four digits of the student ID")
set.seed(1320)
my.p <- round(runif(1), 2)
my.x <- sample(1:10, 2)
my.r <- sample(1:10, 1)
my.alpha <- round(rgamma(1,1,1), 2)
my.beta <- round(rgamma(1,1,1), 2)
library(pracma)
```

# Problem 1

Use the rejection method to find an efficient way to generate a random variable having density function (15%)
$$f(x)=\frac{1}{2}(1+x)e^{-x},0<x<\infty$$


```{r}
f <- function(x) {0.5*(1+x)*exp(-x)}
c_f <- function(x) {(1+x)*exp(x)/8/x^2} #f/g
h <- function(x) {(exp(x)*x^2-2*exp(x))/(8*x^3)} #d f/g
n <- 5000
X <- c()
for (i in 1:n){
   k <- 1
   while (TRUE) {
     Y <- -log(prod(runif(3))) / 2  # Y∼Gamma(3,2)
     U <- runif(1)
     if ( U < c_f(Y)/1.5 ) {  
       X[i] <- Y
       break()
     }
   }
}
plot(density(X), main="", xlab="X")
curve(f, from=0, col="red", add=T)
legend("topright", c("simulation", "exact"), col=c(1,2), lty=1)
```


# Problem 2

Use simulation to approximate the following integrals. (20\%)

(a). $\int_0^1 e^{e^x}dx$  

```{r}
# Ans
# (a)

n <- 50000
u <- runif(n)
h <- function(y){
  a <- 0
  b <- 1
  g <- function(x) exp(exp(x))
  (b-a)*g( a+(b-a)*y )
}
mean(h(u))
fun <- function(x) exp(exp(x))
integral(fun,xmin=0,xmax = 1)
```


(b). $\int_{-2}^2 e^{x+x^2}dx$  

```{r}
# Ans
# (b)
set.seed(1320)
n <- 50000
u <- runif(n)
h <- function(y){
  a <- -2
  b <- 2
  g <- function(x) exp(x+x^2)
  (b-a)*g( a+(b-a)*y )
}
mean(h(u))
fun <- function(x) exp(x+x^2)
integral(fun,xmin=-2,xmax = 2)
```


(c). $\int_0^1 \int_0^1 e^{(x+y)^2}dydx$  

```{r}
# Ans
# (c)
#two-dimension integral
#method1
set.seed(1320)
k <- 80000
gi <- c()
g <- function(x,y) exp((x+y)^2)
for(i in 1:k){
  u <- runif(2)
  u1 <- u[1];u2 <- u[2]
  gi[i] <- g(u1,u2)
}
mean(gi)

fun <- function(x,y) exp((x+y)^2)
integral2(fun,xmin=0,xmax = 1,ymin=0,ymax=1)
```


(d). $\int_0^\infty \int_0^x \exp^{-(x+y)}dydx$


```{r}
# Ans
# (d)
set.seed(1320)
k <- 80000
gi <- c()
g <- function(x,y) exp(-(x+y))
for(i in 1:k){
  u <- runif(2)
  u1 <- u[1];u2 <- u[2]
  gi[i] <- g(u1,u2)
}
mean(gi)
fun <- function(x,y) exp(-(x+y))
ymax <- function(x) 1 - x
integral2(fun,xmin=0,xmax = 1,ymin=0,ymax)
```


# Problem 3

Write a program to generate $B$ values from the probability mass function $\Pr\{X= `r my.x[1]`\} = `r my.p`$ and $\Pr\{X= `r my.x[2]`\} = `r 1-my.p`$. Let $B = 1000$, run the program, and determine the proportion of values that are equal to `r sample(my.x, 1)`.  (10\%)

```{r}
# Ans
p <- c(0.73,0.27)
n <- 1000
k <- c()
u <- runif(n)
x0 <- which(u<p[1])
k[x0] <- 7
x1 <- which((u>=p[1])&(u<sum(p[1:2])))
k[x1] <- 8
table(k)
```


# Problem 4  

Show how to generate a random variable whose distribution function
$$F(x)=1-e^{-(\frac{x}{\alpha})^\beta},0<x<\infty$$
using  

(a) the inverse transform method (10\%) (b) the rejection method. Assume that $\alpha=`r my.alpha`$ and $\beta= `r my.beta`$ (10\%)


## the inverse transform method

```{r}
# Ans 
U <- runif(5000)
alpha<-0.19
beta<-0.01
Y <- (-log(1-U)/alpha)^(1/beta)
plot(density(Y, from=0), main="", xlab="Y")
curve(dexp(x, rate=1), from=0, col="red", add=T)
legend("topright", c("simulation", "exact"), col=c(1,2), lty=1)
```

## the rejection method

```{r}
# Ans 

```
### the max of function is Infinite, X would be 0

# Problem 5  

Give three methods to for generating a Negative Binomial $NB(r=`r my.r`, p=`r my.p`)$ random variable. (15\%)

## method I  

```{r}
# Ans 
set.seed(1320)
my.rnb<-function(r, p) {
  U <- runif(n = r)
  # number of trials
  sum( floor( log(U)/log(1-p) ) + 1)
  # number of failures
  # sum( floor( log(U)/log(1-p) ))
}
B <- 10000
r <- 5
p <- 0.73
X <- c()
for (i in 1:B) {
  X[i]<-my.rnb(r=r, p=p)
}
mean(X) 
mean(rnbinom(B, size = r, prob=p)+r)
```

## method II  

```{r}
# Ans
my.rnb2<-function(r, p){
 pr <- p^r # j=r
 ef <- pr
 U <- runif(1)
 j <- r
 if (U<ef) {
   x <- j
 } else {
  while (U > ef) {
    pr <- ( (j*(1-p))/(j+1-r) )*pr
    ef <- ef+pr
    j <- j+1
  }
  x <- j
 }
 return(x)
}
set.seed(1320)
B <- 1000
r <- 5
Y <- c()
p <- 0.73
for (i in 1:B) {
  Y[i] <- my.rnb2(r=r, p=p)
}
mean(Y)
mean(rnbinom(B, size = r, prob=p)+r)
```

## method III  

```{r}
# Ans 
my.rnb3<-function(r, p){
 pr <- p^r # j=0
 ef <- pr
 U <- runif(1)
 j <- 0
 if (U<ef) {
   x <- j
 } else {
  while (U > ef) {
    pr <- ( ((j+1+r-1)*(1-p))/(j+1) )*pr
    ef <- ef+pr
    j <- j+1
  }
  x <- j
 }
 return(x)
}
set.seed(1320)
B <- 1000
r <- 5
Y <- c()
p <- 0.73
for (i in 1:B) {
  Y[i] <- my.rnb3(r=r, p=p)
}
mean(Y)+r
mean(rnbinom(B, size = r, prob=p)+r)
```


# Problem 6

Give two methods for generating a random variable having density function (20\%)  
$$
f(x)=\left\{
\begin{array}{ccc}
e^{2x} & , & -\infty <x <0 \\
e^{-2x} & , & 0< x < \infty\\
\end{array}
\right.
$$

## Method I:   

```{r}
# Ans 
# Answer
U <- runif(5000)
Y <- -log(1-U)/2
X<- log(1-U)/2
plot(density(Y,from = 0), main="", xlab="Y")
plot(density(c(X,Y)), main="", xlab="Y")
```

## Method II:


```{r}
# Ans
U <- runif(5000)
Y1 <- log(2*U)/2
Y2 <- -log(2-2*U)/2
plot(density(c(Y1,Y2)), main="", xlab="Y")
```
