---
title: "R程式知識整理"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1.基本運算和陣列
```{r}
5+3
5/3
5^3
5**3
5%%3
5%/%3
1:10
seq(1, 10, 2)
seq(1, 10, length.out = 6)
abs(-2)
exp(10)
log(2)
log2(2)
log(10)
log10(10)

```


## 2.一些取整函數
```{r}
round(125.78253)
round(125.78253, digits = -2)
round(83524587, digits = -3)
signif(125.78253, digits = 2)
signif(83524587, digits = 5)
floor(125.78253)
ceiling(125.78253)
trunc(125.78253)
```


## 3.一些統計量會用到的（大概）
```{r}
x <- 1:25
print(x)
mean(x)
var(x)
median(x)
quantile(x, c(0.1, 0.5, 0.7))
x <- c(1:25, NA)
summary(x)
mean(x, na.rm = TRUE)
var(x, na.rm = TRUE)
median(x, na.rm = TRUE)
quantile(x, 0.5, na.rm = TRUE)
par(mfrow = c(1, 2))
boxplot(x)
hist(x)
```


## 4.Vector
```{r}
vt1 <- c(1:5)
print(vt1)
vt2 <- c(3:6)
print(vt2)
vt2 <- c(vt2, vt1)
print(vt2)
length(vt2)
vt1[-2]
vt2[-c(3:6)]
rep(3, 12)
rep(seq(2, 10, 2), 2)
rep(seq(2, 10, 2), rep(3, 5))


colors <- c("red", "yellow", "BLUE")
more.colors <- c(colors, "green", "cyan")
more.colors
substr(more.colors, 1, 3)
grep("y", more.colors)

y.in.V <- grep("y", more.colors)
more.colors[y.in.V]

paste(colors, "line", sep = "" )
paste("I like", colors, collapse = "; ")

```


## 5.Boolean operations
```{r}
A <- c(T, T, F, T, F); B <- c(3, 1, 5, 4, 7)
A
B[A]
B[!A]
sum(A)

```
### 另外有這些可以使用：
is.null() is.na() is.nan() is.infinite() is.character() is.integer() is.numeric()


## 6.matrix
```{r}
a <- 1:5; b <- 6:10;
c <- 11:15; d <- 16:20
M1 <- rbind(a,b,c,d)
M1
dim(M1)
colnames(M1) <- c("V1", "V2", "V3", "V4", "V5")
M1

M1[2, 4]; M1[4, 4];M1[c(2, 4), c(3, 5)]
M1[, 4]; M1[4, ];M1[c(2, 4), ]

M2 <- cbind(a, b, c, d)
M2
dim(M2)

X <- 1:20
matrix(X, nrow = 4, ncol = 5)
matrix(X, nrow = 5, ncol = 4)
matrix(X, nrow = 4, ncol = 5, byrow = TRUE)
matrix(X, nrow = 5, ncol = 4, byrow = TRUE)

```


## 7.Control Flow
### Syntax:
#### for (**index** in vector) **commands**
* ##### index: the index is changed each time
* ##### vector: it includes all possible cases
* ##### commands: actions

### syntax:
#### if(condition) break
* #####The break statement causes the loop to terminate immediately. break statements
can also be used in for() and while() loops.

### syntax:
#### repeat{ statements }
* ##### This causes the statements to be repeated endlessly.

### Syntax:
#### next:
* ##### The next statement causes control to return immediately to the top of the loop; it
can also be used in any loop.

### Syntax:
#### if **(condition)** {commands when TRUE} (else{commands when FALSE})
* ##### The else part is optional, and provides an alternative set of commands
which are to be invoked in case the logical variable is FALSE.

### Syntax:
#### while **(condition)** statements
* ##### If the condition evaluates to FALSE, nothing more is done. If it evaluates to
TRUE the statements are executed, condition is evaluated again, and the
process is repeated.


## 8.Function
#### 就手刻Function（大概）


## 9.Data Frame
### data.frame( )
* ##### Most data sets are stored in R as data frames.
* ##### These are like matrices, but with the columns having their own names.
* ##### Columns can be of different types from each other.
```{r}
colors <- c("red", "yellow", "blue")
numbers <- c(1, 2, 3)
colors.and.numbers <- data.frame(colors, numbers, more.numbers = c(4, 5, 6))
colors.and.numbers

data2 <- data.frame(colors, numbers, more.numbers = c(4, 5, 6),
stringsAsFactors = FALSE)
data2 <- rbind(data2, c("black", 7, 8))
data2
```


## 10.Data input and output
* #### Change the directory: **setwd(“dir”)**
* #### Find the directory: **get()**
* #### Suppose you have constructed some R objects, type **dump(objects, file = “XXX.R”)**
* #### To retrieve the objects in a future session, type **source(“XXX.R”)**
* #### To save all objects in the current workspace, type **save.image(“XXX.RData”)**
* #### To save parts of objects, type **save(a, b, c, file = “XXX.RData”)**
* #### Use **load(“XXX.RData”)** to retrieve data

### You can save a matrix, a vector, or a data frame into two types of file, .txt (.dat) and .csv.
* #### Use **write.table(A, file = “XXX.txt”)**
* #### Use **write.csv(A, file = “XXX.csv”)**

### You can laod a matrix, a vector, or a data frame from two types of file, .txt (.dat) and .csv.
* #### Use **read.table(file = “XXX.txt”)**
* #### Use **read.csv(file = “XXX.csv”)**

### If you read a data from a file with names of columns, you will get different input data of read.table() from that of read.csv().
### With names of columns in a .txt file, you should add **header = TRUE**

### To download a package, type **install.packages(“XXX”)**

### Before using some functions in a downloaded package, you should call the package by typing **library(XXX)**.









